Study of Intra/Inter-Application Interference for Smart Job Allocation on HPC system

### 2015-09-23 submission.tex
the outline of version 2

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{algorithm}
%\usepackage{algorithm2e}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{flushend}
\usepackage{url}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage{caption}
%\usepackage[labelfont=bf]{caption}
\usepackage[font=bf,labelsep=space]{caption}

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/mira}
   \caption{The activity of Mira, IBM BlueGene/Q system at Argonne National Lab. Many jobs runninng concurrently on the system. Different jobs represented by specific colors. }
   \label{fig: mira activity}
\end{figure}

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/amg/amg_ct}
   \caption{Rank-Rank communication topology of AMG with 27 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}.   }
   \label{fig: amg communication topology}
\end{figure}

@@

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/cr/cr10_ct}
   \caption{Rank-Rank communication topology of CrystalRouter with 10 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}. }
   \label{fig: crystalrouter10 communication topology}
\end{figure}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/cr/cr100_ct}
   \caption{Rank-Rank communication topology of CrystalRouter with 100 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}. }
   \label{fig: crystalrouter100 communication topology}
\end{figure}

@@

Here, we provide the communication topology graph of Crystal Router with 10-rank and 100-rank respectively. As we can see from figure \ref{fig: crystalrouter10 communication topology}, every 5-rank is a compact community, where data transfer is very intensive. Beside the "5-rank community", there is "pair-wise" global data transfer in Crystal Router. Obviously, there is data transfer alone the diagnal. When the scale of Crystal Router increase to 100, the "5-rank community" is still the dominant pattern in a multi-stage manner. The same pattern can be observed from the global data transfer. Our observation about the dominant communication pattern of Crystal Router is the multi-stage "5-rank community" and "pair-wise" global data transfer happen recursively as the scale of the application increase.

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/mg/mg125_ct}
   \caption{Rank-Rank communication topology of MultiGrid with 125 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}. }
   \label{fig: multigrid125 communication topology}
\end{figure}

@@

@@

For a job requires $n$ nodes submitted to non-partition based 3D torus-connected system, it gets an allocation of various possible shapes, which could be 3D balanced-cube, 3D unbalanced-cube, 2D mesh, or even 1D list. Figure \ref{fig: allocation} shows some possible allocations for a 64-node job. 3D balanced-cube allocation (in Figure \ref{fig: allocation} as red) is $\{4,4,4\}$, 3D unbalanced-cube allocation is $\{8,4,2\}$(in Figure \ref{fig: allocation} as green), 2D mesh allocation is $\{8,8,1\}$ (in Figure \ref{fig: allocation} as blue).

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.48\textwidth]{Pic/allocationshape/allocation}
  \caption{64-node job with different allocation shapes. Red, Green and Blue represents 3D balanced, 3D unbalanced and 2D allocation respectively. }
  \label{fig: allocation}
\end{figure}

\subsection{Allocation Simulation}
\label{sec:alloc sim}

In this section, we analysis the impact of different allocation strategies on two real applications, AMG and Grystal Router. The torus network performance is determined by its dimensionality and link bandwidth. We evaluate the data transfer time of AMG and Crystal Router on torus network with different dimensionality and link bandwidth configurations in section \ref{sec: dimensionality study}. Then, we will show applications performance on 3D torus network with different allocation strategies in section \ref{sec: alloc strategy study}.

\subsection{Torus Dimensionality}
\label{sec: dimensionality study}

As the increase of the dimensionality of torus netowrk, so does the number of links connected with each node. The increased aggregated bandwidth of each node will definitely reduce the data transfer time of each rank in the application. Figure xxx shows the performance of the AMG and CrystalRouter on a 2K node torus network model with a 3D torus (16x16x8), a 5D torus (8x4x4x4x4), and a 7D torus (4x4x4x4x2x2x2). The bandwidth between nodes is 2GiB/s in one direction, thus, the aggregated bandwidth is 12GiB/s per node in 3D torus, 20GiB/s per node in 5D torus, and 28GiB/s per node in 7D torus. As we can see from the figure, communication time of both applications decrease as the dimensionality of the network increase. The aggregated bandwidth of each node can accelerate the transfer of data. This can justify the fidelity and consistency of the torus network model.
\textcolor{green}{cr1000 on 7D result is missing in Fig\ref{fig: dimenstudy-avgtime} and \ref{fig: dimenstudy-maxtime} , will be added soon.}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/dimenstudy/maxtime}
   \caption{The Percentage of Maximum Time spent to send data over 3D, 5D and 7D torus networks by AMG1728, CrystalRouter1000, MultiGrid1000.}
   \label{fig: dimenstudy-maxtime}
\end{figure}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/dimenstudy/avgtime}
   \caption{The Percentage of Average Time spent to send data over 3D, 5D and 7D torus networks by AMG1728, CrystalRouter1000, MultiGrid1000.}
   \label{fig: dimenstudy-avgtime}
\end{figure}

\textcolor{blue}{sensitivity study of 5D torus with 2GB,4GB,8GB will be added here. }

\textcolor{red}{We can also provide Per-Rank time spent for data transfer. not sure if necessay.}

\section{Interference Analysis}
In this section, we will explore the performance of three applications on different allocations in a 3D torus network. First, we analysis the impact from different allocation shape, then we will present the results by using our communication aware allocation policy.

\subsection{Different Allocation Shape}
As we shown in Fig\ref{fig: allocation}, there could be three differet allocation shape on 3D torus network, namely 3D balanced, 3D un-balanced, and 2D. In this section, we will show the performance of three applications on these three different shape allocations.

There are lots of research work try to design fancy allocation algorithms to provide application with most compact allocation, like using space filling curve (SFC) to index high dimentional cube into one dimensional list. Allocation by cutting chunks of nodes from this one dimensional list will guarantee cubical allocation. However, try to provide cubical allocation without considering application's communication pattern could cause backfire.

\textcolor{red}{Detail explanation will be add for Fig\ref{fig: shapestudy-avgtime}-Fig\ref{fig: shapestudy-mg125}.}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/shapestudy/avgtime}
   \caption{The Percentage of Average Time spent to send data by AMG216, CrystalRouter100, MultiGrid125 with 2D, 3D-unbalanced, 3D-balanced allocation.}
   \label{fig: shapestudy-avgtime}
\end{figure}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/shapestudy/maxtime}
   \caption{The Percentage of Max Time spent to send data by AMG216, CrystalRouter100, MultiGrid125 with 2D, 3D-unbalanced, 3D-balanced allocation.}
   \label{fig: shapestudy-maxtime}
\end{figure}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/shapestudy/amg216_rank_msgtime}
   \caption{(AMG216) Time spent by each rank to send data on 2D, 3D-unbalanced, 3D-balanced allocation. }
   \label{fig: shapestudy-amg216}
\end{figure}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/shapestudy/cr100_rank_msgtime}
   \caption{(CrystalRouter100) Time spent by each rank to send data on on 2D, 3D-unbalanced, 3D-balanced allocation.}
   \label{fig: shapestudy-cr100}
\end{figure}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/shapestudy/mg125_rank_msgtime}
   \caption{(MultiGrid125) Time spent by each rank to send data on 2D, 3D-unbalanced, 3D-balanced allocation.}
   \label{fig: shapestudy-mg125}
\end{figure}

\subsection{Allocation Strategies Study}
\label{sec: alloc strategy study}

We proposed two allocation strategies, Compact and Chunk to study the impact of different allocation the application's performance. The Compact allocation always provides application with a cubical allocation on 3D torus, regardless application's communication pattern. This cubical allocation will keep the locality of the application, all the processes reside on it will have the shortest pair-wise distance.

The Chunk allocation simulation the scenario of non-contiguous allocation strategy employed in production system like Cray XT machines. The traditional non-contiguous allocation simply picks available nodes in spite of their locations and assign them to application. The motivation of non-contiguous allocation act like this is to maximize system utilization, while being blind to application's communication pattern would greatly prolong application's communication time. Although Chunk allocation provides application with non-contigous allocation too, it assign the chunk of nodes in consideration of application's communication pattern. For example, we know the dominant communication pattern of CrystalRouter in section \ref{sec:crystalrouter}, every 5 rank form a community, where intensive communication happens between them. With such knowledge knowledge about application's communication pattern, the Chunk allocation will provide CrystalRouter with allocation that consists of small chunks, the size of which will be at least 5 nodes.

Figure xxx shows the performance of AMG, CrystalRouter and MultiGrid on 3D torus with Compact and Chunk allocation.

\textcolor{red}{The results and figures for this part is not ready yet!!!}

\section{Related Work}
\label{sec:related_work}
Batch scheduling on HPC system has been a hot topic getting constant discussion since the 1990's.
Feitelson et al proposed the most widely used job scheduling policy which is First Come, First Serve (FCFS) combined with 
EASY backfilling\cite{feit}. FCFS/EASY backfilling policy greatly improves HPC system's utilization and cuts the wait time 
of first job in the waiting queue. Since then, many studies seek to refine this classic scheduling paradigm. Tang et al. 
tried to improve the accuracy of user's estimated job runtime and walltime so as to enhance the efficiency of backfilling and  minimize the system fragmentation\cite{wei-ipdps2010} \cite{wei-jpdc2013} \cite{wei-ipdps2011}. % And there are some other variation of FCFS/EASY backfilling proposed to optimize system performance in terms of power consumption and energy cost \cite{zhou}\cite{yang-sc13}.

Only with the information about job size and estimated run time seems to be insufficient for batch scheduler do make the 
optimal scheduling/allocaiton decision. Some work proposed that the batch scheduler should be aware of some information 
about system network information in order to fully utilize system resources.Leung et al. presented allocation strategies 
based on space filling curves and one dimensional packing \cite{leung}. The problem with using space filling curve is that  
it can only be applied to system with the scale of $2^n$ nodes in each dimension, which is a ideal case that not existing 
in morden HPC systems. Albing et al. conducted study about the allocation strategies that the Cray
Application Level Placement Scheduler (ALPS) used \cite{carl-cug}. The job allocation in Cray Linux Environment (CLE) 
operating system is managed by ALPS, which simply works off an ordered node list, however that is ordered.

Based on their 
work, Yang et al. presented a window-based locality-aware job scheduling design for torus-connected system
\cite{yang-cluster14}. In this new scheduling framework, several jobs are taken into  consideration at the same time for job 
prioritizing and resource allocation. A list of slots is maintained to preserve node contiguity information for
resource allocation. Each job been assigned into one of these slot so that the locality can be mostly preserved.

Rosenthal et al. found there is limited benefit for many applications by
increasing network bandwidth \cite{rosenthal}. They employed a subset of the
CORAL mini-applications that represent U.S. Department of Energy workload and
leverage multirail networkings to evaluate the improvement of these applications
caused by increased network bandwidth. The applications that send mostly small
messages or larger messages asynchronously are not bandwidth bounded, hence,
benefit only slightly or not at all from increased bandwidth.

Hoefler et al. propose to use performance modeling techniques to analysis 
factors that impact the performance of parallel scientific applications 
\cite{hoefler-modeling}. However, as the scale of HPC continue grows, the 
interference of concurrently running jobs is getting worse, which is hard to be 
quantified by performance profiling tools.

Bogdan et al provide a set of guidelines how to configure a network with 
Dragonfly topology for workload with Nearest Neighbor communication 
pattern\cite{Bogdan-hpdc14}. They first derived a theoretical model of Nearest 
Neighbor communication performance on Dragonfly network that can predict network 
bottleneck. Then, they use simulation to validate the correctness of their 
theoretical model.

Dong et al describe IBM Blue Gene/Q's 5D torus interconnect
network\cite{Dong-SC11}. They developed simple benchmarks that conforms to four
different communication patterns, namely ping-pong, nearest neighbor, broadcast
and allredcue, to demonstrate the effectiveness of this highly parallel 5D torus
network.

>>>>

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{algorithm}
%\usepackage{algorithm2e}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{flushend}
\usepackage{url}
\usepackage{xcolor}
\usepackage{amsmath}
%\usepackage{subfig}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage[labelfont=bf]{caption}
\usepackage[font=bf,labelsep=space]{caption}

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.2\textwidth}
        \centering
        \includegraphics[height=1.2in]{figs/goodallocation}
        \caption{God.}
        \label{fig:overview_sub1}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.2\textwidth}
        \centering
        \includegraphics[height=1.2in]{figs/badallocation}
        \caption{Bad.}
        \label{fig:overview_sub2}
    \end{subfigure}%
   \caption{Indication of multiple jobs running on Cray system. Many jobs runninng concurrently on the system. Different jobs represented by specific colors.}
   \label{fig: overview}
\end{figure}

%\begin{figure}[h!] 
%  \centering
%  \includegraphics[width=0.38\textwidth]{figs/mira}
%   \caption{The activity of Mira, IBM BlueGene/Q system at Argonne National Lab. Many jobs runninng concurrently on the system. Different jobs represented by specific colors. }
%   \label{fig: mira activity}
%\end{figure}

@@

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/amg/amg_pip}
   \caption{Rank-Rank communication topology of AMG with 27 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}.   }
   \label{fig: amg communication topology}
\end{figure}

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/cr/cr_pip}
   \caption{Rank-Rank communication topology of CrystalRouter with 100 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}. }
   \label{fig: crystalrouter100 communication topology}
\end{figure}

@@

As we can see from figure \ref{fig: crystalrouter100 communication topology}, every 5-rank is a compact community, where data transfer is very intensive. Beside the "5-rank community", there is "pair-wise" global data transfer in Crystal Router. Obviously, there is data transfer alone the diagnal. When the scale of Crystal Router increase to 100, the "5-rank community" is still the dominant pattern in a multi-stage manner. The same pattern can be observed from the global data transfer. Our observation about the dominant communication pattern of Crystal Router is the multi-stage "5-rank community" and "pair-wise" global data transfer happen recursively as the scale of the application increase.

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/mg/mg_pip}
   \caption{Rank-Rank communication topology of MultiGrid with 125 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}. }
   \label{fig: multigrid125 communication topology}
\end{figure}

@@

The torus network performance is determined by its dimensionality and link bandwidth. As the increase of the dimensionality of torus netowrk, so does the number of links connected with each node. The increased aggregated bandwidth of each node will definitely reduce the data transfer time of each rank in the application. Figure \ref{fig: dimenstudy} shows the performance of the AMG, CrystalRouter and MultiGrid on a 2K node torus network model with a 3D torus (16x16x8), a 5D torus (8x4x4x4x4), and a 7D torus (4x4x4x4x2x2x2). The bandwidth between nodes is 2GiB/s in one direction, thus, the aggregated bandwidth is 12GiB/s per node in 3D torus, 20GiB/s per node in 5D torus, and 28GiB/s per node in 7D torus. As we can see from these figures, communication time of both applications decrease as the dimensionality of the network increase. The increased aggregated bandwidth of each node can accelerate the transfer of data. This can justify the fidelity and consistency of the torus network model. The same pattern can be found in Figure \ref{fig:bandwidthstudy}, as the bandwidth increase from 2GiB/s, to 4GiB/s and 8GiB/s in the 5D torus network, the data transfer time can be greatly reduced.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.2\textwidth}
        \centering
        \includegraphics[height=1.2in]{figs/dimenstudy/avgtime}
        \caption{Normalized Average Time.}
        \label{fig:1sub1}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.2\textwidth}
        \centering
        \includegraphics[height=1.2in]{figs/dimenstudy/maxtime}
        \caption{Normalized Max Time.}
        \label{fig:1sub2}
    \end{subfigure}%
   \caption{Normalized time spent to send data over 3D, 5D and 7D torus networks by AMG1728, CrystalRouter1000, MultiGrid1000.}
   \label{fig: dimenstudy}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.2\textwidth}
        \centering
        \includegraphics[height=1.3in]{figs/bandwidthstudy/avgtime}
        \caption{Normalized Average Time.}
        \label{fig:2sub1}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.2\textwidth}
        \centering
        \includegraphics[height=1.3in]{figs/bandwidthstudy/maxtime}
        \caption{Normalized Max Time.}
        \label{fig:2sub2}
    \end{subfigure}%
   \caption{Normalized time spent to send data over 5D torus with 2GB/s, 4GB/s and 8GB/s bandwidth by AMG1728, CrystalRouter1000, MultiGrid1000.}
   \label{fig:bandwidthstudy}
\end{figure}

%\begin{figure}[h!] 
%  \centering
%  \includegraphics[width=0.38\textwidth]{figs/bandwidthstudy/maxtime}
%   \caption{The Normalized Max Time spent to send data over 5D torus with 2GB/s, 4GB/s and 8GB/s bandwidth by AMG1728, CrystalRouter1000, MultiGrid1000.}
%   \label{fig: bandwidthstudy-maxtime}
%\end{figure}
%
%\begin{figure}[h!] 
%  \centering
%  \includegraphics[width=0.38\textwidth]{figs/bandwidthstudy/avgtime}
%   \caption{The Normalized Average Time spent to send data over 5D torus with 2GB/s, 4GB/s and 8GB/s bandwidth by AMG1728, CrystalRouter1000, MultiGrid1000.}
%   \label{fig: bandwidthstudy-avgtime}
%\end{figure}

\section{Interference Analysis}
\textbf{presents results of single app running with con/non-cont allocation}
In this section, we will explore the communication interference. First, we will analysis the application's intra-job interference by assigning each job different shapes of allocation. All these allcoation are contigous in their dimensionality.

@@

\subsection{Intra-Job Interference Analysis}
\label{sec: introjob}

To study the intra-job interference of each job, we simulate each job running on 3D torus network with different allocation shapes. We assign each application with three different shapes allocation, i.e. 3D balanced-cube, 3D unbalanced-cube, 2D mesh. Figure \ref{figs/cont/allocation} shows some possible allocations for a 64-node job. 3D balanced allocation is $\{4,4,4\}$ as red, 3D unbalanced allocation is $\{8,4,2\}$ as green, 2D allocation is $\{8,8,1\}$ as blue.

Figure \ref{fig: differentshape-time} shows the data transfter time of three applications running with three different allocation ships.

%There are lots of research work try to design fancy allocation algorithms to provide application with most compact allocation, like using space filling curve (SFC) to index high dimentional cube into one dimensional list. Allocation by cutting chunks of nodes from this one dimensional list will guarantee cubical allocation. However, try to provide cubical allocation without considering application's communication pattern could cause backfire.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.2\textwidth}
        \centering
        \includegraphics[height=1.2in]{figs/intra-job/shapestudy/avgtime}
        \caption{Normalized Average Time.}
        \label{fig:shape-sub1}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.2\textwidth}
        \centering
        \includegraphics[height=1.2in]{figs/intra-job/shapestudy/maxtime}
        \caption{Normalized Max Time.}
        \label{fig:shape-sub2}
    \end{subfigure}%
   \caption{Normalized time spent to send data by AMG216, CrystalRouter100, MultiGrid125 with 2D, 3D-unbalanced, 3D-balanced allocation.}
   \label{fig: differentshape-time}
\end{figure}

%\begin{figure}[h!] 
%  \centering
%  \includegraphics[width=0.38\textwidth]{figs/shapestudy/amg216_rank_msgtime}
%   \caption{(AMG216) Time spent by each rank to send data on 2D, 3D-unbalanced, 3D-balanced allocation. }
%   \label{fig: shapestudy-amg216}
%\end{figure}
%
%\begin{figure}[h!]
%  \centering
%  \includegraphics[width=0.38\textwidth]{figs/shapestudy/cr100_rank_msgtime}
%   \caption{(CrystalRouter100) Time spent by each rank to send data on on 2D, 3D-unbalanced, 3D-balanced allocation.}
%   \label{fig: shapestudy-cr100}
%\end{figure}
%
%\begin{figure}[h!] 
%  \centering
%  \includegraphics[width=0.38\textwidth]{figs/shapestudy/mg125_rank_msgtime}
%   \caption{(MultiGrid125) Time spent by each rank to send data on 2D, 3D-unbalanced, 3D-balanced allocation.}
%   \label{fig: shapestudy-mg125}
%\end{figure}
Then, we simulate each application running on 3D torus with contiguous allocation and non-contiguous allocation. For non-contiguous allocation we set the chunk size to 10 in order to preserve application's locality. Figure \ref{fig: non-cont-vs-cont} shows the data transfer time of application running with contiguous and non-contiguous allocation.

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/intra-job/non-cont-vs-cont}
   \caption{Three Applications running exclusively on 3D torus with contigous and non-contiguous allocation}
   \label{fig: non-cont-vs-cont}
\end{figure}

\subsection{Inter-Job Interference Analysis}
\label{sec: interjob ference study}

\begin{figure}[t!]
    \centering
    \begin{subfigure}[t]{0.2\textwidth}
        \centering
        \includegraphics[height=1.2in]{figs/cont/allocation}
        \caption{Contiguous}
        \label{fig:cont_sub1}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.2\textwidth}
        \centering
        \includegraphics[height=1.2in]{figs/inter-job/noncont/sharing}
        \caption{Non-contiguous}
        \label{fig:noncont_sub1}
    \end{subfigure}%
%    \hspace{1em}%
%    \begin{subfigure}[t]{0.2\textwidth}
%        \centering
%        \includegraphics[height=1.2in]{figs/inter-job/noncont/exclusive}
%        \caption{"Exclusive Mode".}
%        \label{fig:noncont_sub2}
%    \end{subfigure}
    \caption{(a) Illustrates the contiguous allocation in different shape. (b) Illustrates the non-contiguous allocation with chunk of size 4.}
\end{figure}

In order to analysis the interference between concurrently runing jobs, we simulate three application running concurrently on the same 3D network.  We assign each application with a non-contiguous set of small chunk of nodes, 'chunk' refers to a small number(like 4) of adjacent nodes as shown in Figure \ref{fig:noncont_sub1}. The chunk belongs to one application is next to each other. The "chunk" size is critical to the application's performance. Figure\ref{fig: chunk_size} shows the results of applications' data transfer time with different chunk size.

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/inter-job/noncont/chunk_size}
   \caption{The Normalized Time spent to send data by AMG216, CrystalRouter100, MultiGrid125 with different chunk size.}
   \label{fig: chunk_size}
\end{figure}

\section{Related Work}
\label{sec:related_work}

P1: tools for monitoring and profiling

P2: communication pattern

P3: Interference between concurrently running jobs

P4: Job allocation(little bit)
